\section{AI Impact}

\subsection{Ayo}
My experience using AI/LLMs was a educational experience. Upon encountering our first roadblock. My team decided to assign me the technical task of learning how testing works. At first, understanding it myself was quite a challenege as I was completely unfamiliar with the Javascript testing framwork. The LLM was able to break up the code i produced and give me sample test cases I could use for testing. Another way LLMs helped me was in understanding how css components integrate into testing and the necessary field attributes that go into the test file and running it in the console.

\subsection{Jonathan}
I chose to limit my use of AI/LLMs for this application as often the code it produced did not work smoothly due to the complexity of the project. When developing the game logic, using AI/LLMs became more of a hassle than a tool as I spent more time debugging than actually programming. However, AI/LLMs were particularly useful for CSS, as my knowledge of CSS was quite limited before the project was started. 

\subsection{Brett}
Throughout the project, I found myself using AI quite a bit for various reasons. Whenever I ran into bugs or when things weren’t working as expected, I’d turn to AI for debugging help. AI was also a big help when it came to styling with css. However, getting AI to understand exactly what I wanted design-wise was a little tricky. I often had to go back and forth with multiple prompts to narrow down what I wanted. Besides that, anytime I had questions while coding, I would use AI for quick answers. Overall, AI was an extremely valuable tool throughout the project and made the overall process much smoother.