\section{Introduction}

%[[ No more than one page that provides a short project description and then
%sets the stage for the rest of the document. ]]

%This sentence has an example citation~\cite{DBLP:journals/infsof/BinkleyMI22}

In today's increasingly rapid changing digital world, keeping users engaged is essential to making interactive applications successful. To keep users engaged, they must feel connected and entertained. Our client seeks to develop an engaging, real-time multiplayer card game, to engage users and improve long-term user retention. The application overall should provide compelling game play experience with social interaction and an easy to understand user interface. 


To address our clients needs, we proposed an extensive software solution that leverages modern web development technologies. The application features a responsive and dynamic front end built using HTML, CSS, and JavaScript with React. React's component based architecture allows us to create reusable modules that ensures consistency and streamlines development as each component can be developed independently. All of the React components we build return HTML that can be dynamically injected into our main HTML file. The program logic is handled appropriately depending on the purpose the code serves. Each component handles its necessary back-end logic locally and at the end returns the necessary HTML for the front-end.  Non-react component files do not return any HTML for the front-end such as the JavaScript Class that establishes the deck and card structures. Additionally, by using Firebase, we ensure real time data synchronization and built-in authentication, both necessary for a seamless multiplayer experience. 


Key features our application include, Real-Time Gameplay, Engaging user Experience, User Authentication, and Social Interaction. Each of these features is necessary to delivering an immersive experience for the users. Real-Time Gameplay ensures all players at a game table receive the same instant updates and feedback, crucial for maintaining the flow of the game. An engaging user experience includes a visually appealing, intuitive, and responsive interface, all necessary to retaining users. The front end is built using HTML, CSS, JavaScript and React, which allows us to create a highly dynamic user interface. The inclusion of user authentication is necessary to allow for socialization and a friend system in the application. As multiplayer games rely on social interaction, our application includes features that encourage social interactions between players through the friends and chats system.


This document serves a detailed roadmap for the development of the multiplayer card game War for our client Cosmic Radiance. It starts by outlining the requirements of the software to identify the needs of the application. Additionally, this section will provide an overview of the different requirements of each user type. The following section provides a detailed look at each Iteration (sprint) of the project. Each iteration subsection will cover the proposed plan for the sprint, activities, testing, and a retrospective. The System Architecture and Design section focuses on the design considerations that influenced the project's chosen technologies. The Testing section focuses on the testing process throughout the development of the application, as well as the overall coverage. 
 
 
  




