\section{Reflections on the Project}
\begin{enumerate}
    \item What would you have done differently if you started the project today with your current knowledge? 
    \item What were the main barriers? 
    \item How well organized was the team?
    \item Did you have a leader, would/did a leader help keep the team on track?
    \item A summary of what you learned about Software Engineering process.
\end{enumerate}


\subsection{Ayo}
\begin{enumerate}
    \item I would take more time understanding different frameworks and tools such as React and Jest instead of just starting the project immediately 
    \item Understanding how different testing environments work alongside the jest framework
    \item The team was very organized, as we met frequently outside class and kept constant communication
    \item Yes, it helped everyone understand the deadlines and what they needed to complete during the sprint
    \item I learned how communication and effective collaboration are equally or more important than technical expertise. The full Software Development Life Cycle can be quite tedious, therefore working in a team that understands each others strengths and weaknesses is very important to effective work, Roadblocks are inevitable, learning how to adjust and workaround as a team is very important
\end{enumerate}

\subsection{Jonathan}
\begin{enumerate}
    \item I would take more time designing the project and make detailed diagrams to define an architecture before development. 
    \item Testing was a challenge. 
    \item The team maintained good communication, with frequent meetings.
    \item Yes, having a leader helped the timeline of the project move along. 
    \item I learned that software engineering process involves a significant amount of preparation before writing code. I also gained first hand experience on why it involves so much preparation during the development of this application. 
\end{enumerate}

\subsection{Brett}
\begin{enumerate}
    \item I would have begin the project extra early in order to compensate for unknown roadblocks
    \item Testing was tricky, especially with Firebase.
    \item Team was organized and maintained consistent communication throughout the sprints.
    \item Yes, it made sure everyone was on track and moving smoothly
    \item I learned the value of breaking tasks into user stories, which made the project more manageable. This approach helped streamline the process and ensured that each feature or functionality was clearly defined. Additionally, I gained experience working effectively on a group project by maintaining clear communication, and collaborating through GitHub.
\end{enumerate}








