\subsection{Non-Functional Requirements}

\subsubsection{Category: User Interface}
\textbf{ID: Navigation and Design Consistency}
\begin{enumerate}
    \item Description: Ensured the website was easy to navigate for new users by implementing clear and intuitive buttons. Consistent color schemes were applied across the entire website to create a cohesive and user-friendly interface.
    \item Affects: Maintains a unified design throughout the website allowing for visual consistency.
\end{enumerate}
\vspace{1em}
\textbf{ID: Responsive Design}
\begin{enumerate}
    \item Description: Implemented a responsive design for the website, ensuring the user interface adjusts seamlessly to different screen sizes. This feature allows the application to function effectively on various screen size without disrupting usability.
    \item Affects: Grants a greater user experience as the website maintains a consistent and intuitive interface regardless of screen size.
\end{enumerate}
\vspace{1em}
\textbf{ID: Error Messages}
\begin{enumerate}
    \item Description: Implemented proper error messages for scenarios such as login and signup failures. These messages provided clear feedback to users, such as invalid credentials or missing fields, to guide them in correcting their actions and improving their overall experience.
    \item Affects: Enhances the user experience as they are able to clearly understand why there may be an issue.
\end{enumerate}
\subsubsection{Category: Security}
\textbf{ID: Passwords}
\begin{enumerate}
    \item Description: Firebase automatically hashes passwords during the authentication process, ensuring secure storage of user credentials in the database.
    \item Affects: reduces the risk of data breaches by securely storing hashed passwords.
\end{enumerate}
\vspace{1em}
\subsubsection{Category: Performance}
\textbf{ID: Quick Loading Times}
\begin{enumerate}
    \item Description: Ensured the website quickly loaded the lobby, game screens, and chat messages, achieving a response time of under 1 second for these critical features. This optimization enhanced the real-time user experience and reduced wait times during navigation and interactions.
    \item Affects: Grants the user a better experience by providing a seamless and responsive interface, keeping users engaged.
\end{enumerate}
